---
title: "Wake County Food Inspections"
output:
  pdf_document:
    keep_md: yes
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
```

# Wake County Restaurants and their Sanitation Scores

## Objective

The aim of this Project is to help Wake County residents make informed decisions
about where they eat by providing them with a list of restaurants with
sanitation scores above 90 (excellent) and a list of restaurants with
sanitation scores below 80 (unacceptable). This will be done by exploring two
data sets that Wake County has made available to the public: the Restaurants in
Wake County data set, and the Food Inspections data set. The list presented to
Wake County citizens will include the names, addresses, and phone numbers of the
aforementioned restaurants.


## Restaurants

The table below contains information about all of the restaurants in Wake
County. Each restaurant has a HSISID, which serves as a unique identifier. Other
information contained in the table includes the restaurants' names, addresses,
phone numbers, and the dates of their opening.

```{r}
restaurants_file <- "Restaurants_in_Wake_County.csv"
Restaurants <- read_csv(restaurants_file)
Restaurants
```

## Sanitation Scores

The table below contains the sanitation scores of all of the restaurants in Wake
County. Each restaurant is identified by its HSISID, which serves as a key to
access more information about the restaurant in the Restaurants data table.

```{r}
inspections_file <- "Food_Inspections.csv"
Inspections <- read_csv(inspections_file)
Inspections
```

## IDs of Restaurants with Sanitation Scores Above 90

The algorithm below filters the Inspections table for the HSISIDs of all of the
restaurants in Wake County that have sanitation scores above 90, and stores the
result as a list.

```{r}
ids_above_90 <- Inspections[Inspections$SCORE <= 90, "HSISID"]
ids_above_90 <- as.list(ids_above_90$HSISID)
```

## IDs of Restaurants with Sanitation Scores Below 80

The algorithm below filters the Inspections table for the HSISIDs of all of the
restaurants in Wake County that have sanitation scores below 80, and stores the
result as a list.

```{r}
ids_below_80 <- Inspections[Inspections$SCORE <= 80, "HSISID"]
ids_below_80 <- as.list(ids_below_80$HSISID)
```

## Restaurants with Sanitation Scores Above 90

The Restaurants table is filtered for names, addresses, and phone numbers of the
restaurants in Wake County that have sanitation scores above 90.


```{r}
restaurants_above_90 <- Restaurants[Restaurants$HSISID %in% ids_above_90,
                              c("NAME","ADDRESS1", "CITY", "STATE", "POSTALCODE",
                                "PHONENUMBER")]
restaurants_above_90
```

## Restaurants with Sanitation Scores Below 80

The Restaurants table is filtered for names, addresses, and phone numbers of the
restaurants in Wake County that have sanitation scores below 80.


```{r}
restaurants_below_80 <- Restaurants[Restaurants$HSISID %in% ids_below_80,
                              c("NAME","ADDRESS1", "CITY", "STATE", "POSTALCODE",
                                "PHONENUMBER")]
restaurants_below_80
```

